---
title: "Problem and solution for advanced R"
author: "Yong Qiao"
date: "9/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download the source file. 

Hadley Wickham's book, Advanced R. He provide source code for this book. <https://github.com/hadley/adv-r>.

First we Clone with HTTPS using the following link in local computer <https://github.com/hadley/adv-r.git>

## Start compile

Download the package 'sloop' and 'emo' from github
```{r }
devtools::install_github("hadley/sloop")
devtools::install_github("hadley/emo")
```

##error massage:
Quitting from lines 4-5 (Introduction.Rmd) Error in dev.control(displaylist = if (record) "enable" else "inhibit") : dev.control() called without an open graphics device Calls: local ... call_block -> block_exec -> chunk_device -> dev.control
solved by 
1. install xquartz
2. install Macports
3. Using MacPorts, the port is called 'cairo', run  sudo port install cairo in command window
4. install package 'tinytex', 'posterdown'

## error massage:
Quitting from lines 535-550 (R6.Rmd) 
Error in loadNamespace(name) : there is no package called 'RSQLite'
```{r}
install.packages("RSQLite",repos = "http://cran.us.r-project.org")
```

## error massage
Quitting from lines 38-40 (Perf-measure.Rmd) 
Error in library(profvis) : there is no package called 'profvis'

```{r }
install.packages('profvis',repos = "http://cran.us.r-project.org")
```

## error massage
uitting from lines 38-40 (Perf-measure.Rmd) 
Error in library(bench) : there is no package called 'bench'
Calls: local ... withCallingHandlers -> withVisible -> eval -> eval -> library
Error: `ggbeeswarm` must be installed to use `type = "beeswarm"` option.


```{r}
install.packages('bench',repos = "http://cran.us.r-project.org")
install.packages('ggbeeswarm',repos = "http://cran.us.r-project.org")
install.packages('Inconsolata',repos = "http://cran.us.r-project.org")

```
## error massage
Package fontspec Error: The font "Inconsolata" cannot be found.

solution: download required package  inconsolata from and install it to computer https://github.com/MihailJP/Inconsolata-LGC/downloads

```{r}
bookdown::render_book("./index.Rmd", output_format = "bookdown::pdf_book")
```
We can open the pdf
```{r}
# install.packages('fs',repos = "http://cran.us.r-project.org")

library(fs)
file_show(path(getwd(), "_book/_main.pdf"))
```

